6.867 Problem Set 1

### 2015-12-08 Latex/Paper.tex
[project] write a little, add a gitignore.

A similar study by Berger and Milkman (2012) \cite{BergerMilkman12} examines the relationship between content and word-of-mouth virality. They find that the emotional content of a NYT article is predictive of its virality. Using simple measures of an article's sentiment and emotionality, Berger and Milkman show that positive articles are more likely to show up on the New York Times "Most-Emailed" list. They also show that articles that evoke high physiological positive or negative arousal (such as awe or anger) tend to be more viral than articles that evoke deactivating emotions (sadness). We build on this study in two ways: first, we relate an article's content back to the number of page views it receives rather than its virality\footnote{Which companies arguably care more about since word-of-mouth virality is usually a means to increase page views}. Second, we employ more sophisticated machine learning feature extraction techniques to see if they work any better over their simple measures.
%------------------------------------------------

@@

We limit our dataset to consist of pages that only contain articles or blogposts published during the month of August. We parse the data to obtain a list of urls, which need to be stripped of potential garbage. After cleaning up the url data, we are left with 6682 unique pieces of content. We then parse our dataset and aggregate the number of counts each url receives. In order to make the comparison between articles fairer since an article that's been out longer will have more page views on average, we only count the number of page views received up to 7 days after publication\footnote{Given that page views tend to sharply drop off soon after publication since recency is quite important to the News, the number of page views obtained during the 7 days after an article is published represents the vast majority (usually well over 90\%) of total page views an article receives.}. In total, our data consists of over 250 million page views. As seen in Figure 1 below, the distribution of page views is highly skewed with very have tables. After applying a log transformation (as seen in Figure 2), our distribution looks considerably more normal.

@@

\subsection{Subsection}

\begin{table}[hbt]
\caption{Table of Grades}
\centering
\begin{tabular}{llr}
\toprule
\multicolumn{2}{c}{Name} \\
\cmidrule(r){1-2}
First name & Last Name & Grade \\
\midrule
John & Doe & $7.5$ \\
Richard & Miles & $2$ \\
\bottomrule
\end{tabular}
\label{tab:label}
\end{table}

\begin{description}
\item[Word] Definition
\item[Concept] Explanation
\item[Idea] Text
\end{description}

\subsubsection{Subsubsection}

\begin{itemize}[noitemsep] % [noitemsep] removes whitespace between the items for a compact look
\item First item in a list
\item Second item in a list
\item Third item in a list
\end{itemize}

\subsubsection{Subsubsection}

\subsection{Subsection}

@@

So long and thanks for all the fish \cite{Figueredo:2009dg}.

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------
\phantomsection
\bibliographystyle{unsrt}
\bibliography{sample}

>>>>

A similar study by Berger and Milkman (2012) \cite{berger2012makes} examines the relationship between content and word-of-mouth virality. They find that the emotional content of a NYT article is predictive of its virality. Using simple measures of an article's sentiment and emotionality, Berger and Milkman show that positive articles are more likely to show up on the New York Times "Most-Emailed" list. They also show that articles that evoke high physiological positive or negative arousal (such as awe or anger) tend to be more viral than articles that evoke deactivating emotions (sadness). We build on this study in two ways: first, we relate an article's content back to the number of page views it receives rather than its virality\footnote{Which companies arguably care more about since word-of-mouth virality is usually a means to increase page views}. Second, we employ more sophisticated machine learning feature extraction techniques to see if they work any better over their simple measures.
%------------------------------------------------

@@

We limit our dataset to consist of pages that only contain articles or blogposts published during the month of August. We parse the data to obtain a list of urls, which need to be stripped of potential garbage. After cleaning up the url data, we are left with 6682 unique pieces of content. We then parse our dataset and aggregate the number of counts each url receives. In order to make the comparison between articles fairer since an article that's been out longer will have more page views on average, we only count the number of page views received up to 7 days after publication\footnote{Given that page views tend to sharply drop off soon after publication since recency is quite important to the News, the number of page views obtained during the 7 days after an article is published represents the vast majority (usually well over 90\%) of total page views an article receives.}. In total, our data consists of over 250 million page views. As seen in Figure 1 below, the distribution of page views is highly skewed with very heavy tails. After applying a log transformation (as seen in Figure 2), our distribution looks considerably more normal.

@@

In preparing to perform our regression, we construct a number of features, using both the parsed NYT article data and secondary sources. These features include the Flesch reading ease, the (guessed) gender of the author(s), the popularity of the author(s), the sentiment of the article text, the perplexity of the article text, and variables indicating the section the article appeared in and the article's content type. Found below is a full list of these features, as well as the methodology used to construct them and validation of the features, where appropriate.

\begin{description}
	\item[Flesch Reading Ease] The Flesch reading ease is a metric developed by Flesch in 1948 \cite{flesch1948new}. The score indicates how difficult a piece of English text is to understand. Lower scores correspond to more difficult passages, and the highest score attainable is 120.0. The formula for calculating a passage's Flesch reading ease is

	\begin{equation}
	206.835 - 1.015 \left ( \frac{\textrm{\# words}}{\textrm{\# sentences}} \right ) - 84.6 \left ( \frac{\textrm{\# syllables}}{\textrm{\# words}} \right )
	\end{equation}

	To calculate the Flesch reading ease, we use the python library ``textstat." Despite the fact that the above formula is relatively straightforward, the task of counting the number of syllables in a block of text is non-trivial, so we rely on ``textstat" to do so accurately. In cases where the Flesch reading ease was for some reason null (e.g., a blog post containing only a picture), we assign the Flesch reading ease its median value.

	\item[Author Popularity] We attempt to include some measure of a particular author's popularity. It stands to reason that a new article by Paul Krugman or A.O. Scott should garner more readership than a new article by an unknown graduate student enrolled in 6.867 at MIT!

	In order to measure something that will serve as a decent proxy for popularity, we programmatically searched for every distinct author in our dataset using Bing, and recorded the number of search results that were returned by the query. In cases where a particular article has more than one distinct author, we calculate an ``effective" popularity by simply calculating the average number of search results over all article authors.

	\item[Author Gender] We also attempt to construct a feature that indicates the most likely gender of the article author(s). In cases where the gender of the author is unclear (e.g., Robin) or there are likely multiple authors with different genders (e.g., The New York Times Staff), we record a third gender value, ``ambiguous / unknown."

	We construct our gender data by cross-referencing the first names of all of the authors in our dataset against U.S. Social Security Administration baby name data from 1935 to 1997. If over 90\% of the babies with a given name have been male, we assume a given author is male. If over 90\% of the babies with a given name have been female, we assume a given author is female. Otherwise, we record ``ambiguous / unknown."

	\item[Material Type, Section, Desk, and Article Type] We also include dummy variables including the material type (e.g., `News' or `Obituary'), desk (e.g., `Weekend' or `Real Estate'), article type (`Blog post' or `Article'), and section (e.g., `Movies' or `World').

\end{description}

We also include features that attempt to capture the article sentiment and the article text perplexity. Since the construction of these features was more involved and involved validation of our algorithms, we discuss these two features in separate subsections.

\subsection{Article Sentiment}

\subsubsection{Article Perplexity}

@@

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------
\phantomsection
\bibliographystyle{unsrt}
\bibliography{Paper}
